Porting the Steel Bank Common Lisp Compiler and Runtime to the Nintendo Switch NX Platform

### 2025-05-19 els2025-sbcl-nx/presentation.tex
Add some more issues we had to face.

\begin{frame}
  \frametitle{Relocation (cont.)}
  \begin{itemize}
    \item Solution: Relocate all Lisp spaces on start up
    \item \Rightarrow{} Problem for NX: Code generation hardwires some primitive
      object addresses.
    \item Solution: Change codegen to be position independent.
    \item Code objects in SBCL also contain Lisp pointers (constants)
    \item \Rightarrow{} Problem for NX: Relocation and moving GC needs to fix up
      these constants, but code objects are not writable
    \item Solution: Segregate code instructions and data in code
      objects into different ELF sections offline, rewrite code
      instructions to reference r/w section
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Garbage Collection}
  \begin{itemize}
  \item Garbage collection on SBCL on non-Windows platforms uses POSIX
    signals to stop-the-world.
  \item \Rightarrow{} Problem for NX: No POSIX signals.
  \item Solution: Use safepoints (implemented already on Windows)
  \item BUT: The safepoint mechanism still uses virtual memory
    hardware exceptions to stop the current thread
  \item \Rightarrow{} Problem for NX: No ability to handle operating system
    exceptions
  \item Solution: Change safepoint codegen to poll state flags
    explicitly
  \end{itemize}
\end{frame}

>>>>

\begin{frame}
  \frametitle{Relocation (cont.)}
  \begin{itemize}
    \item Solution: Relocate all Lisp spaces on start up (support
    existed for most Lisp spaces already, except for one)
    \item \Rightarrow{} Problem for NX: Code generation hardwires some primitive
      object addresses.
    \item Solution: Change codegen to be position independent.
    \item Code objects in SBCL also contain Lisp pointers (constants)
    \item \Rightarrow{} Problem for NX: Relocation and moving GC needs to fix up
      these constants, but code objects are not writable
    \item Solution: Segregate code instructions and data in code
      objects into different ELF sections offline, rewrite code
      instructions to reference r/w section
  \end{itemize}
\end{frame}

@@

\begin{frame}
  \frametitle{Garbage Collection}
  \begin{itemize}
  \item Garbage collection on SBCL on non-Windows platforms uses POSIX
    signals to stop-the-world.
  \item \Rightarrow{} Problem for NX: No POSIX signals.
  \item Solution: Use safepoints (implemented already on Windows)
  \item BUT: The safepoint mechanism still uses virtual memory
    hardware exceptions to stop the current thread
  \item \Rightarrow{} Problem for NX: No ability to handle operating system
    exceptions
  \item Solution: Change safepoint codegen to poll state flags
    explicitly (challenge: do this in a race-free way!)
  \end{itemize}
\end{frame}
